Review Paper Draft

### 2020-06-29 main.tex
Figures: updating with figures for independent subpopulations, xi = 0.8. Labels still need work.

Given the superior performance of PC-Lasso and LMM-Lasso compared to the naive lasso in the presence of environmental confounding, we next compared these methods in the presence of two forms of simulated population structure: (1) relatedness characterized by a small number of large subpopulations to model large-scale environmental heterogeneity or population stratification, similar to that described in our motivating air quality example, and (2) a large number of small, closely related subpopulations to approximate finer grained environmental heterogeneity, such as household exposures or behavioral norms. Figure \ref{fig:kinship} illustrates the simulated kinship structures in these scenarios, as well as that present in the empirical SNP data. We note that we show results for simulated data generated such that subpopulations are of equal size, while the empirical SNP data illustrates a scenario of unequal subpopulation sizes.

@@

\anna{
\begin{itemize}
    \item "Spend" this many figures on kinship?
\end{itemize}
}

\pb{these are nice figures, but to me, better for supplement}

\begin{figure}[H]
\begin{subfigure}{.8\textwidth}
  \centering
  % include first image
  \includegraphics[width=.7\linewidth]{figures/kinship1}  
  \caption{Independent subpopulations simulated kinship; a small number of large groups}
  \label{fig:large_groups}
\end{subfigure}
\newline
\begin{subfigure}{.8\textwidth}
  \centering
  % include second image
  \includegraphics[width=.7\linewidth]{figures/kinship2}  
  \caption{Independent subpopulations simulated kinship; a large number of small groups}
  \label{fig:small_groups}
\end{subfigure}
\newline
\begin{subfigure}{.8\textwidth}
  \centering
  % include second image
  \includegraphics[width=.7\linewidth]{figures/vanderwas_kinship.pdf}  
  \caption{\anna{Vanderbilt data genome-wide} kinship}
  \label{fig:vandy_groups}
\end{subfigure}
\caption{\anna{obviously these figures need to be tweaked:sizes, uniform scales}}
\label{fig:kinship}
\end{figure}

@@

\begin{figure}[H]
    \centering
    % \includegraphics[scale = 0.9]{figures/mse_diff_subpops}
     \includegraphics[scale = 0.9]{figures/mse_diff_subpops.png}
    \caption{Relative performance of LMM-Lasso, PC-Lasso in terms of estimation accuracy:  \anna{$\bgamma$ structure is nonlinear (aka half and half) and heterogeneous, $\eta= \xi = 0.5$}}
    \label{fig:big_vs_small}
\end{figure}

@@

\anna{replace this with inedpendent subpopulations}
\begin{figure}[H]
    \centering
    % \includegraphics[scale = 0.9]{figures/fig2b.png}
    \includegraphics[scale = 0.9]{figures/mse_diff_hetero.png}
    \caption{Relative performance of LMM-Lasso, PC-Lasso for different subpopulation and $\bgamma$ structures: \anna{structureX is 1d linear admixture, $\eta= \xi = 0.5$}}
    \label{fig:big_small_gamma}
\end{figure}

@@

\anna{Fix factor label greek letters - R update broke some things}
\begin{figure}[H]
    \centering
    \includegraphics[scale = 1]{figures/eta_beta_hat.png}
     \caption{Caption goes here \anna{$\xi = 0.5$, structureX = 1d linear, structureGamma is half and half heterogeneous}}
    \label{fig:eta_beta_mse}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[scale = 0.8]{figures/time_ratio.png}
    \caption{Caption goes here \anna{$\eta = \xi = 0.5$, structureX = 1d linear, structureGamma is half and half heterogeneous}}
    \label{fig:time}
\end{figure}

>>>>

Given the superior performance of PC-Lasso and LMM-Lasso compared to the naive lasso in the presence of environmental confounding, we next compared these methods in the presence of two forms of simulated population structure: (1) relatedness characterized by a small number of large subpopulations to model large-scale environmental heterogeneity or population stratification, similar to that described in our motivating air quality example, and (2) a large number of small, closely related subpopulations to approximate finer grained environmental heterogeneity, such as household exposures or behavioral norms.

\anna{the following sentence needs to change now that kinship figs are gone}
Figure \anna{KINSHIP FIGS IN SUPP NOT HERE} illustrates the simulated kinship structures in these scenarios, as well as that present in the empirical SNP data. We note that we show results for simulated data generated such that subpopulations are of equal size, while the empirical SNP data illustrates a scenario of unequal subpopulation sizes.

@@

@@

\begin{figure}[H]
    \centering
    % \includegraphics[scale = 0.9]{figures/mse_diff_subpops}
     \includegraphics[scale = 0.9]{figures/mse_diff_subpops.png}
    \caption{Relative performance of LMM-Lasso, PC-Lasso in terms of estimation accuracy:  \anna{structureX is independent subpops, $\bgamma$ structure is dichotomous and heterogeneous, $\eta= 0.5, \xi$ is varying}}
    \label{fig:big_vs_small}
\end{figure}

@@

\begin{figure}[H]
    \centering
    % \includegraphics[scale = 0.9]{figures/fig2b.png}
    \includegraphics[scale = 0.9]{figures/mse_diff_hetero.png}
    \caption{Relative performance of LMM-Lasso, PC-Lasso for different subpopulation and $\bgamma$ structures: \anna{structureX is independent subpops, $\eta= 0.5, \xi = 0.8$}}
    \label{fig:big_small_gamma}
\end{figure}

@@

\anna{Fix factor label greek letters - R update broke some things}
\begin{figure}[H]
    \centering
    \includegraphics[scale = 1]{figures/eta_beta_hat.png}
     \caption{Caption goes here \anna{$\xi = 0.5$, structureX = independent subpops, structureGamma is dichotomous heterogeneous, large blocks}}
    \label{fig:eta_beta_mse}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[scale = 0.8]{figures/time_ratio.png}
    \caption{Caption goes here \anna{$\eta = 0.5, \xi = 0.8$, structureX = independent subpops, structureGamma is dichotomous heterogeneous, large blocks}}
    \label{fig:time}
\end{figure}
